Meta-analytic evidence that sexual selection improves population fitness

### 2019-04-12 Manuscripts/Manuscript_MetaAnalysis.Rmd
Editorial changes the SI formatting, citations and abstract now 150 words

---
title: '\huge{Meta-analytic evidence that sexual selection improves population fitness}'
author: 
- Justin G. Cally\textsuperscript{§*}, Devi Stuart-Fox\textsuperscript{§} and Luke Holman\textsuperscript{§}
- '\textsuperscript{§}School of BioSciences, The University of Melbourne, Parkville, VIC, 3052, Australia'
- '\textsuperscript{*}\textit{justin.g.cally@gmail.com}'
output:
  pdf_document:
    keep_tex: true
bibliography: Bibliography/Bibliography.bib
subparagraph: yes
urlcolor: blue
csl: Bibliography/NComms.csl
header-includes: \usepackage{microtype} \usepackage[all]{hypcap} \usepackage{amsmath}
  \usepackage{booktabs} \usepackage{caption} \usepackage[labelfont=bf]{caption} \usepackage{titling}
  \pretitle{\begin{flushleft}\LARGE} \posttitle{\par\end{flushleft}\vskip 0.5em} \preauthor{\begin{flushleft}\large
  \lineskip 0.5em} \postauthor{\par\end{flushleft}} \predate{\begin{flushleft}\large}
  \postdate{\par\end{flushleft}} \usepackage{fancyhdr} \pagestyle{fancy} \fancyhead[LO,LE]{\textsl{\leftmark}}
  \rhead[]{Sexual selection improves fitness} \usepackage{titlefoot}
  \usepackage{amssymb} \usepackage{rotating} \usepackage{lineno} \linenumbers \usepackage{setspace}\onehalfspacing
    \usepackage{titlesec} \titleformat{\section}{\normalfont\scshape\LARGE}{\thesection}{1em}{} \titleformat{\subsection}{\normalfont\Large}{\thesubsection}{1em}{} \titleformat{\subsubsection}{\normalfont\large}{\thesubsubsection}{1em}{} \usepackage{abstract} \renewcommand{\abstractnamefont}{\normalfont\Large} 
    \usepackage{hyperref}\hypersetup{colorlinks=true, linkcolor=blue, filecolor=blue, urlcolor=blue} 
    \usepackage{color,soul}
    \raggedbottom    
abstract: Sexual selection has manifold ecological and evolutionary consequences, making its net effect on population fitness difficult to predict from first principles. Instead, one can empirically determine whether sexual selection increases or decreases population fitness by manipulating the opportunity for sexual selection in replicate populations, allow evolution to proceed, and then compare the evolved average fitness between the treatment groups. Here, we synthesise 459 effect sizes from 65 pertinent experimental evolution studies using meta-analysis. We find evidence that sexual selection on males tends to elevate the mean and reduce the variance for many fitness traits, especially in females evolving under stressful conditions. However, sexual selection had weaker positive effects on direct measures of population fitness, such as extinction rate and proportion of viable offspring, than on individual fitness measures with indirect or less clear relationships to population fitness. Overall, we conclude that the beneficial population-level consequences of sexual selection typically outweigh the harmful ones and that the effects of sexual selection on total selection, genetic variance, and/or evolvability can differ markedly between sexes and environments. We discuss the implications of these results for conservation and evolutionary biology.
---
\pagestyle{plain}

@@

Sexual selection, defined as selection resulting from competition for mates or their gametes [@RN139], is a ubiquitous evolutionary force that has profoundly shaped the natural world. As far back as Darwin [@RN310], researchers have theorised that sexual selection can change the average absolute fitness of individuals in a population, henceforth termed ‘population fitness’ [@RN269; @RN268]. However, opinion is divided over whether the net effect on population fitness is positive or negative [@RN42; @RN25; @RN116; @RN95]. _Prima facie_, one might predict that sexual selection would have no effect on population fitness, since it does not matter which individuals of the faster-reproducing sex (typically males) succeed in mating, so long as some do [@RN142]. However, when genotypes with high mating or fertilisation success also have superior breeding values for traits that affect population fitness (*e.g.*, survival, parental care, female fecundity, or success in interspecific competition), sexual selection is predicted to elevate population fitness by causing a correlated response in these other traits [@RN95]. In essence, the demographically-limiting sex (typically females) benefits from a gene pool that has been purged of harmful alleles through sexual selection on the non-limiting sex (typically males). Theoretically, the benefit to population fitness could be large [@RN94; @RN198; @RN58].

Conversely, sexual selection can decrease population fitness if male sexually-selected traits are negatively genetically correlated with female fitness, producing intralocus sexual conflict [@RN187; @RN146; @RN237; @RN147; @Harano_2010; @Plesnar_2014]. Additionally, sexual selection frequently favours phenotypes that reduce population fitness but benefit the individuals expressing them, such as harassment or infanticide by mate-seeking males [@RN6; @RN267; @RN37], as well as investment in costly sexual signals and weaponry at the expense of parental care: \textit{inter}locus sexual conflict [@RN314; @RN276; @RN315]. Given these conflicting theoretical expectations and empirical results, it remains unclear whether sexual selection tends to have a net benefit or cost to population fitness [@RN42; @RN25; @RN116; @RN95].

@@

The effect size estimates we recovered were highly heterogeneous ($I^2$ = 95.2%, 95% CIs: 94.4% to 95.9%), reflecting the large differences in experimental procedures, study species, and fitness components included in our meta-analysis [@RN208; @Senior_I2_2016]. Heterogeneity stemmed mostly from between-study differences ($I^2_{study}$ = 36%, 95% CIs: 26.5% to 45.4%) rather than differences between fitness components and taxon ($I^2_{fitness\:components}$ = 0.4%, 95% CIs: 0.2% to 0.9%; $I^2_{taxon}$ = 1.4%, 95% CIs: 0.2% to 3.5%). Variation among taxa is explored further in the Supplementary Information (\href{https://justincally.github.io/SexualSelection/#restricted_analysis_of_just_the_higher-quality_data}{Supplementary Figure 2, Supplementary Table 10}).  \phantomsection

@@

The results of the meta-analysis support predictions that sexual selection on males can improve population fitness and accelerate adaptation [@RN94; @RN173; @RN54; @RN141; @RN230; @RN198; @RN58]. One possible mechanism is that male mating success is positively genetically correlated with traits that contribute to population fitness, allowing females to benefit from a genome that has been purged of deleterious alleles through competition between males [@RN94; @RN198; @RN95]. A second (non-exclusive) mechanism is that experimental manipulation of sexual selection on males might directly alter the selective pressures acting on females, causing female traits to evolve. For example, removing sexual selection via enforced monogamy probably alters selection on females, because it alters the frequency of interactions with males (as well as the evolved genotype of those males). What is less clear is why the manipulation of sexual selection had a larger effect on female trait means and variances as opposed to males -- this result is arguably the opposite of what one would expect, since it is males that experience stronger sexual selection. Below we discuss possible explanations for this result, in light of the core principle that the extent of adaptation depends on additive genetic (co)variance and the strength of selection [@RN317; @RN318].

@@

Our results suggest that the greater benefit of sexual selection to females than males is magnified in stressful environments. Recent work has emphasised that environmental stress should reduce the strength of sexually antagonistic selection relative to selection that is concordant between sexes. Theoretical models reaching this conclusion [@RN67; @RN173] have been supported by some empirical work [@RN187; @RN74; @RN243]; for example, one study found that high fitness males produced low fitness daughters under benign conditions but high fitness daughters under stress [@RN74]. However, other quantitative genetic studies have shown that stressful conditions do not always reduce sexual antagonism [@RN297; @RN200; @RN257]. Variation in effects of sexual selection in stressful environments may be due to potentially variable responses amongst taxa [@RN298] and environments. Notably, Connallon & Hall [@RN173] predict that the dynamics of environmental change alter the strength of sexual antagonism; for instance, gradual directional selection may facilitate indefinite sexual antagonism, while rapid cyclical change can swiftly remove it. Our meta-analysis suggests that under directional selection imposed by environmental stress, sexual antagonism is likely dampened; allowing sexual selection to facilitate adaptation and persistence.

@@

Our findings have implications for fundamental and applied research. For example, the beneficial population-level consequences of sexual selection have been proposed as one possible resolution to the long-standing evolutionary puzzle regarding sexual reproduction [@RN309]. If sufficiently strong, these benefits can more than compensate for the costs of sexual reproduction, and prevent sexual populations from being outcompeted by asexual mutants [@RN94; @RN308; @RN198]. Sexual selection is also important for conservation [@RN25] and captive breeding programs [@RN117]. Within captive breeding programs, genetic diversity is often managed through the enforced monogamy of a strategically selected (genetically diverse) breeding pair [@RN117]. Captive breeding programs may benefit from allowing sexual selection of 'good genes' or more compatible genes [@RN294], or by increasing maternal investment by females paired with attractive males [@RN291; @RN292; @RN293]. Additionally, our findings imply that anthropogenic environmental changes that reduce the opportunity for sexual selection, such as eutrophication, pesticides, artificial light and noise pollution, could reduce the genetic quality of the population, and potentially compromise its long-term persistence [@RN332; @RN331; @RN47; @RN333; @RN330]. Equally, our results support recent evidence that human activities that directly counteract sexual selection, such as selective harvesting of the largest or most ornamented males, can lower population fitness [@RN334]. Based on the weight of evidence from experimental evolution, we suggest that sexually-selected populations may be more resilient to environmental change, including anthropogenic environmental pressures, over relevant time scales. \phantomsection

@@

In addition to the data used to calculate effect size, we collected a set of moderator variables for each paper (see \href{https://justincally.github.io/SexualSelection/#data_extraction_and_effect_size_calculation}{the source data} and associated Supplementary Information). The moderators were selected due to their ready availability, and because we hypothesised that they might explain some of the observed heterogeneity in effect size. A key moderator was whether the environmental conditions that a population evolved under were stressful (*e.g.*, elevated mutation load, novel/sub-optimal food source, increased sub-lethal temperatures). Additionally, we collected details for each effect size on: sex (male, female or a mixed sample of both), taxon (flies, beetles, mice, nematodes, mites, crickets and guppies), the presence/absence of blind methodology, and number of generations a treatment group underwent experimental evolution. In the interests of creating a useful data resource, we also recorded details about each experiment that were not formally analysed due to a shortage of data, such as the type of sexual selection that was manipulated (pre-copulatory, post-copulatory, or both) and the male to female ratio, which is included in the Supplementary Information (\href{https://justincally.github.io/SexualSelection/#data_extraction_and_effect_size_calculation}{the source data}).  \phantomsection

@@

We tested for publication bias via funnel plots, using Egger’s test to quantify plot asymmetry [@RN213; @RN214]. Additionally, we tested for time-lag bias [@RN216], in which effect size magnitudes decline over time as more data are collected. Additionally, we assessed a potential source of publication bias through the correlation between effect size and journal impact factor [@RN217], which can arise if null or countervailing results are more difficult to publish (impact factors were from *InCites Journal Citation Reports*).\phantomsection

@@

All data are freely available on Github (https://github.com/JustinCally/SexualSelection). The repository provides a source data file that was used to create all results, tables and figures. \phantomsection

@@

\textbf{Figure 1: The effect of sexual selection on direct, indirect and ambiguous fitness components.} The effect sizes used in this meta-analysis ($n$ = 459) were grouped into either direct, indirect or ambiguous measures of fitness. Overall, effect sizes were more often positive than negative. Predicted average values are presented as a diamond with 95 % CIs for each fitness-relationship category. The estimates presented here are from REML models with the grand mean across all effect sizes ($\beta$ = 0.25) shown as the blue dotted line. Predictions from both Bayesian and REML models can be found in Supplementary Table 6 and source data are provided at \url{https://github.com/JustinCally/SexualSelection}.

\textbf{Figure 2: The roles of environmental stress and sex.} (a) Sexual selection tends to increase the population mean values of fitness traits, especially for female traits and for populations living under stressful conditions. (b) Under stressful conditions, sexual selection tends to reduce the phenotypic variance in fitness traits, especially for traits measured in females or mixed-sex individuals. The points with error bars show the mean effect sizes and their 95% CIs, determined from a meta-regression fit using restricted maximum likelihood (REML); the point sizes are proportional to the number of effect sizes (see Supplementary Tables 14,18). Results from Bayesian meta-regression are shown as posterior prediction density curves, with vertical lines indicating the median. Source data are provided at \url{https://github.com/JustinCally/SexualSelection}.

\textbf{Figure 3: Tests for publication bias in the dataset.} Tests of publication bias are mixed and suggest publication bias may be present. (a) Inspection and statistical tests of the funnel plot reveal large amounts of heterogeneity in the dataset with asymmetry from increased low-powered, large effect studies. (b) No significant correlation exists between journal impact factor and effect size, (c) additionally there is no significant correlation between effect size and year of publication when testing for the time-lag bias. For (b) and (c) point size is proportional to the precision of the effect size (*i.e.* the inverse of its variance). For (a), the dashed red lines represent the 95 % CIs of the grand mean estimate for all effect sizes and the black dotted and dashed lines depict the 95 % and 99.8 % CIs for the dataset. The grey envelopes in (b) and (c) represent the 95 % CI of the linear regression. Source data are provided at \url{https://github.com/JustinCally/SexualSelection}.

>>>>

---
title: '\huge{Meta-analytic evidence that sexual selection improves population fitness}'
author: 
- Justin G. Cally\textsuperscript{§*}, Devi Stuart-Fox\textsuperscript{§} and Luke Holman\textsuperscript{§}
- '\textsuperscript{§}School of BioSciences, The University of Melbourne, Parkville, VIC, 3052, Australia'
- '\textsuperscript{*}\textit{justin.g.cally@gmail.com}'
output:
  pdf_document:
    keep_tex: true
bibliography: Bibliography/Bibliography.bib
subparagraph: yes
urlcolor: blue
csl: Bibliography/NComms.csl
header-includes: \usepackage{microtype} \usepackage[all]{hypcap} \usepackage{amsmath}
  \usepackage{booktabs} \usepackage{caption} \usepackage[labelfont=bf]{caption} \usepackage{titling}
  \pretitle{\begin{flushleft}\LARGE} \posttitle{\par\end{flushleft}\vskip 0.5em} \preauthor{\begin{flushleft}\large
  \lineskip 0.5em} \postauthor{\par\end{flushleft}} \predate{\begin{flushleft}\large}
  \postdate{\par\end{flushleft}} \usepackage{fancyhdr} \pagestyle{fancy} \fancyhead[LO,LE]{\textsl{\leftmark}}
  \rhead[]{Sexual selection improves fitness} \usepackage{titlefoot}
  \usepackage{amssymb} \usepackage{rotating} \usepackage{lineno} \linenumbers \usepackage{setspace}\onehalfspacing
    \usepackage{titlesec} \titleformat{\section}{\normalfont\scshape\LARGE}{\thesection}{1em}{} \titleformat{\subsection}{\normalfont\Large}{\thesubsection}{1em}{} \titleformat{\subsubsection}{\normalfont\large}{\thesubsubsection}{1em}{} \usepackage{abstract} \renewcommand{\abstractnamefont}{\normalfont\Large} 
    \usepackage{hyperref}\hypersetup{colorlinks=true, linkcolor=blue, filecolor=blue, urlcolor=blue} 
    \usepackage{color,soul}
    \raggedbottom    
abstract: Sexual selection has manifold ecological and evolutionary consequences, making its net effect on population fitness difficult to predict. A powerful empirical test is to experimentally manipulate sexual selection and then determine how population fitness evolves. Here, we synthesise 459 effect sizes from 65 experimental evolution studies using meta-analysis. We find that sexual selection on males tends to elevate the mean and reduce the variance for many fitness traits, especially in females and in populations evolving under stressful conditions. Sexual selection had weaker effects on direct measures of population fitness such as extinction rate and proportion of viable offspring, relative to traits that are less closely linked to population fitness. Overall, we conclude that the beneficial population-level consequences of sexual selection typically outweigh the harmful ones and that the effects of sexual selection can differ between sexes and environments. We discuss the implications of these results for conservation and evolutionary biology. 
---
\pagestyle{plain}

@@

Sexual selection, defined as selection resulting from competition for mates or their gametes [@RN139], is a ubiquitous evolutionary force that has profoundly shaped the natural world. As far back as Darwin [@RN310], researchers have theorised that sexual selection can change the average absolute fitness of individuals in a population, henceforth termed ‘population fitness’ [@RN269]. However, opinion is divided over whether the net effect on population fitness is positive or negative [@RN42; @RN25; @RN116; @RN95]. _Prima facie_, one might predict that sexual selection would have no effect on population fitness, since it does not matter which individuals of the faster-reproducing sex (typically males) succeed in mating, so long as some do [@RN142]. However, when genotypes with high mating or fertilisation success also have superior breeding values for traits that affect population fitness (*e.g.*, survival, parental care, female fecundity, or success in interspecific competition), sexual selection is predicted to elevate population fitness by causing a correlated response in these other traits [@RN95]. In essence, the demographically-limiting sex (typically females) benefits from a gene pool that has been purged of harmful alleles through sexual selection on the non-limiting sex (typically males). Theoretically, the benefit to population fitness could be large [@RN94; @RN198; @RN58].

Conversely, sexual selection can decrease population fitness if male sexually-selected traits are negatively genetically correlated with female fitness, producing intralocus sexual conflict [@RN187; @RN146; @RN147; @Harano_2010; @Plesnar_2014]. Additionally, sexual selection frequently favours phenotypes that reduce population fitness but benefit the individuals expressing them, such as harassment or infanticide by mate-seeking males [@RN37], as well as investment in costly sexual signals and weaponry at the expense of parental care: \textit{inter}locus sexual conflict [@RN276; @RN315]. Given these conflicting theoretical expectations and empirical results, it remains unclear whether sexual selection tends to have a net benefit or cost to population fitness [@RN42; @RN25; @RN116; @RN95].

@@

The effect size estimates we recovered were highly heterogeneous ($I^2$ = 95.2%, 95% CIs: 94.4% to 95.9%), reflecting the large differences in experimental procedures, study species, and fitness components included in our meta-analysis [@RN208; @Senior_I2_2016]. Heterogeneity stemmed mostly from between-study differences ($I^2_{study}$ = 36%, 95% CIs: 26.5% to 45.4%) rather than differences between fitness components and taxon ($I^2_{fitness\:components}$ = 0.4%, 95% CIs: 0.2% to 0.9%; $I^2_{taxon}$ = 1.4%, 95% CIs: 0.2% to 3.5%). Variation among taxa is explored further in the Supplementary Information (\href{https://justincally.github.io/SexualSelection/#restricted_analysis_of_just_the_higher-quality_data}{Supplementary Figure 2 and Supplementary Table 10}).  \phantomsection

@@

The results of the meta-analysis support predictions that sexual selection on males can improve population fitness and accelerate adaptation [@RN94; @RN173; @RN54; @RN230; @RN198; @RN58]. One possible mechanism is that male mating success is positively genetically correlated with traits that contribute to population fitness, allowing females to benefit from a genome that has been purged of deleterious alleles through competition between males [@RN94; @RN198; @RN95]. A second (non-exclusive) mechanism is that experimental manipulation of sexual selection on males might directly alter the selective pressures acting on females, causing female traits to evolve. For example, removing sexual selection via enforced monogamy probably alters selection on females, because it alters the frequency of interactions with males (as well as the evolved genotype of those males). What is less clear is why the manipulation of sexual selection had a larger effect on female trait means and variances as opposed to males -- this result is arguably the opposite of what one would expect, since it is males that experience stronger sexual selection. Below we discuss possible explanations for this result, in light of the core principle that the extent of adaptation depends on additive genetic (co)variance and the strength of selection [@RN317; @RN318].

@@

Our results suggest that the greater benefit of sexual selection to females than males is magnified in stressful environments. Recent work has emphasised that environmental stress should reduce the strength of sexually antagonistic selection relative to selection that is concordant between sexes. Theoretical models reaching this conclusion [@RN67; @RN173] have been supported by some empirical work [@RN187; @RN74]; for example, one study found that high fitness males produced low fitness daughters under benign conditions but high fitness daughters under stress [@RN74]. However, other quantitative genetic studies have shown that stressful conditions do not always reduce sexual antagonism [@RN200; @RN257]. Variation in effects of sexual selection in stressful environments may be due to potentially variable responses amongst taxa [@RN298] and environments. Notably, Connallon & Hall [@RN173] predict that the dynamics of environmental change alter the strength of sexual antagonism; for instance, gradual directional selection may facilitate indefinite sexual antagonism, while rapid cyclical change can swiftly remove it. Our meta-analysis suggests that under directional selection imposed by environmental stress, sexual antagonism is likely dampened; allowing sexual selection to facilitate adaptation and persistence.

@@

Our findings have implications for fundamental and applied research. For example, the beneficial population-level consequences of sexual selection have been proposed as one possible resolution to the long-standing evolutionary puzzle regarding sexual reproduction [@RN309]. If sufficiently strong, these benefits can more than compensate for the costs of sexual reproduction, and prevent sexual populations from being outcompeted by asexual mutants [@RN94; @RN198]. Sexual selection is also important for conservation [@RN25] and captive breeding programs [@RN117]. Within captive breeding programs, genetic diversity is often managed through the enforced monogamy of a strategically selected (genetically diverse) breeding pair [@RN117]. Captive breeding programs may benefit from allowing sexual selection of 'good genes' or more compatible genes [@RN294], or by increasing maternal investment by females paired with attractive males [@RN291; @RN292; @RN293]. Additionally, our findings imply that anthropogenic environmental changes that reduce the opportunity for sexual selection, such as eutrophication, pesticides, artificial light and noise pollution, could reduce the genetic quality of the population, and potentially compromise its long-term persistence [@RN332; @RN331; @RN47; @RN333]. Equally, our results support recent evidence that human activities that directly counteract sexual selection, such as selective harvesting of the largest or most ornamented males, can lower population fitness [@RN334]. Based on the weight of evidence from experimental evolution, we suggest that sexually-selected populations may be more resilient to environmental change, including anthropogenic environmental pressures, over relevant time scales. \phantomsection

@@

In addition to the data used to calculate effect size, we collected a set of moderator variables for each paper (see the Source Data file and associated Supplementary Information). The moderators were selected due to their ready availability, and because we hypothesised that they might explain some of the observed heterogeneity in effect size. A key moderator was whether the environmental conditions that a population evolved under were stressful (*e.g.*, elevated mutation load, novel/sub-optimal food source, increased sub-lethal temperatures). Additionally, we collected details for each effect size on: sex (male, female or a mixed sample of both), taxon (flies, beetles, mice, nematodes, mites, crickets and guppies), the presence/absence of blind methodology, and number of generations a treatment group underwent experimental evolution. In the interests of creating a useful data resource, we also recorded details about each experiment that were not formally analysed due to a shortage of data, such as the type of sexual selection that was manipulated (pre-copulatory, post-copulatory, or both) and the male to female ratio, which is included in the Source Data file.  \phantomsection

@@

We tested for publication bias via funnel plots, using Egger’s test to quantify plot asymmetry [@RN213]. Additionally, we tested for time-lag bias [@RN216], in which effect size magnitudes decline over time as more data are collected. Additionally, we assessed a potential source of publication bias through the correlation between effect size and journal impact factor [@RN217], which can arise if null or countervailing results are more difficult to publish (impact factors were from *InCites Journal Citation Reports*).\phantomsection

@@

All data are freely available on Github (https://github.com/JustinCally/SexualSelection). Additionally, the source data used in this meta-analysis is provided as a Source Data file alongside this manuscript. \phantomsection

@@

\textbf{Figure 1: The effect of sexual selection on direct, indirect and ambiguous fitness components.} The effect sizes used in this meta-analysis ($n$ = 459) were grouped into either direct, indirect or ambiguous measures of fitness. Overall, effect sizes were more often positive than negative. Predicted average values are presented as a diamond with 95 % CIs for each fitness-relationship category. The estimates presented here are from REML models with the grand mean across all effect sizes ($\beta$ = 0.25) shown as the blue dotted line. Predictions from both Bayesian and REML models can be found in Supplementary Table 6. Data used for generating this figure are available in the Source Data file.

\textbf{Figure 2: The roles of environmental stress and sex.} (a) Sexual selection tends to increase the population mean values of fitness traits, especially for female traits and for populations living under stressful conditions. (b) Under stressful conditions, sexual selection tends to reduce the phenotypic variance in fitness traits, especially for traits measured in females or mixed-sex individuals. The points with error bars show the mean effect sizes and their 95% CIs, determined from a meta-regression fit using restricted maximum likelihood (REML); the point sizes are proportional to the number of effect sizes (see Supplementary Tables 14,18). Results from Bayesian meta-regression are shown as posterior prediction density curves, with vertical lines indicating the median. Data used for generating this figure are available in the Source Data file.

\textbf{Figure 3: Tests for publication bias in the dataset.} Tests of publication bias are mixed and suggest publication bias may be present. (a) Inspection and statistical tests of the funnel plot reveal large amounts of heterogeneity in the dataset with asymmetry from increased low-powered, large effect studies. (b) No significant correlation exists between journal impact factor and effect size, (c) additionally there is no significant correlation between effect size and year of publication when testing for the time-lag bias. For (b) and (c) point size is proportional to the precision of the effect size (*i.e.* the inverse of its variance). For (a), the dashed red lines represent the 95 % CIs of the grand mean estimate for all effect sizes and the black dotted and dashed lines depict the 95 % and 99.8 % CIs for the dataset. The grey envelopes in (b) and (c) represent the 95 % CI of the linear regression. Data used for generating this figure are available in the Source Data file.

### 2019-04-12 meta_analysis_sexual_selection_pop_fitness.Rmd
Minor tweaks
Editorial changes the SI formatting, citations and abstract now 150 words

```{r, warning=FALSE}
read.csv('data/outcome.descriptions.csv', fileEncoding="UTF-8") %>%
  kable("html") %>% kable_styling() %>%
  scroll_box(width = "100%", height = "500px")
```
<br></br>

#### References for Supplementary Table 1
```{r, warning=FALSE}
read.csv('data/references.tableS1.csv', fileEncoding="UTF-8") %>%
  kable("html") %>% kable_styling() %>%
  scroll_box(width = "100%", height = "250px")
```
<br></br>

@@

```{r}
read.csv('data/Eligibility Workbook.csv', fileEncoding="UTF-8") %>%
  kable("html") %>% kable_styling() %>%
  scroll_box(width = "100%", height = "500px")
```
<br></br>

@@

**Supplementary Table 13:** Hypothesis tests for the Bayesian model are similar to the REML model (Supplementary Table 8), with slight differences to CIs.

@@

##Effects of environment and sex on direct fitness components

>>>>

```{r, warning=FALSE}
read.csv('data/outcome.descriptions.csv', fileEncoding="UTF-8") %>% select(-Examples) %>%
  kable("html") %>% kable_styling() %>%
  scroll_box(width = "100%", height = "500px")
```
<br></br>

@@

```{r}
read.csv('data/Eligibility Workbook.csv', fileEncoding="UTF-8") %>% 
  mutate(Citation = paste0('[@',Citation,']')) %>%
  kable("html") %>% kable_styling() %>%
  scroll_box(width = "100%", height = "500px")
```
<br></br>

@@

**Supplementary Table 13:** Hypothesis tests for the Bayesian model are similar to the REML model, with slight differences to CIs.

@@

###Effects of environment and sex on direct fitness components
